19Q2

### 2019-05-20 19Q2.Rmd
update Rmds

g2p_dgl <-  as.character(unique(g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)]))
g2p_dg <- as.character(unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)]))
g2p_gl <- as.character(unique(g2p$Gene_Lin[!is.na(g2p$Gene_Lin)]))
g2p_drugs <- as.character(unique(g2p$Drug[!is.na(g2p$Drug)]))
g2p_genes <- as.character(unique(g2p$Gene[!is.na(g2p$Gene)]))
g2p_lins <- as.character(unique(g2p$group_general_lineage_name[!is.na(g2p$group_general_lineage_name)]))
```

@@

```{r fusion_calls, eval=TRUE}
fusions <- read.delim("./data_munging/19Q2/CCLE_fusions.csv.gz", header = TRUE, sep = ",")
fusions$LeftGene <- gsub(" .*", "", fusions$LeftGene)
fusions$RightGene <- gsub(" .*", "", fusions$RightGene)
fusions$X.FusionName <- gsub("--", "-", fusions$X.FusionName)
fusions <- select(fusions, DepMap_ID, X.FusionName)
fusions <- as.data.frame(lapply(fusions, function(x) gsub("IGH@|IGH-@", "IGH", x)))
colnames(fusions) <- c("DepMap_ID", "FusionPair")
fusions <- merge(fusions, ccl_meta, by = "DepMap_ID", all.x = TRUE)
```

@@

@@

# Define color scale
col_fun <- colorRamp2(c(0, 1, 100), c("gray97", "mistyrose", "purple4"))
# Legend properties list
ht_legend_list <- list(legend_direction = "horizontal", legend_width = unit(2.5, "in"), border = "gray70")
ht <- Heatmap(g2p_dg_counts, 
              name = "Number of G2P interpretations",
              col = col_fun,
              na_col = "gray97",
              rect_gp = gpar(col = "gray70"),
              heatmap_legend_param = ht_legend_list,
              cluster_rows = FALSE, 
              cluster_columns = FALSE, 
              show_row_names = FALSE,
              row_names_side = "left",
              row_names_gp = gpar(fontsize = 10),
              column_names_side = "bottom",
              column_names_gp = gpar(fontsize = 10),
              show_column_names = FALSE,
              bottom_annotation = HeatmapAnnotation(
                  text = anno_text(colnames(g2p_dg_counts),
                                   rot = 45,
                                   gp = gpar(fontsize = 10),
                                   offset = unit(1, "npc"),
                                   just = "right"),
                  annotation_height = unit(0.45, "in")),
              row_title = "Drugs",
              row_title_gp = gpar(fontface = "bold", fontsize = 14),
              column_title = "Genes", 
              column_title_gp = gpar(fontface = "bold", fontsize = 14),
              column_title_side = "bottom")

@@

WilcoxonTestDF <- function(dataframe, grouping, outfile) {
  require(ggpubr)
  if("Drug_Gene_Lin" %in% grouping) {
    # Filter out DGLs with too few samples in at least one mutation status category
    count_mut_n <- dataframe %>% count(Drug_Gene_Lin, Mutation) %>% filter(n >= 3)
    count_mut_category <- count_mut_n %>% count(Drug_Gene_Lin) %>% filter(n == 2)
    dgl_keep <- intersect(count_mut_n$Drug_Gene_Lin, count_mut_category$Drug_Gene_Lin)
    dataframe <- filter(dataframe, Drug_Gene_Lin %in% dgl_keep)
    dataframe$Drug_Gene_Lin <- as.character(dataframe$Drug_Gene_Lin)
  }
  signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
  signif <- adj_signif(signif, alpha = 0.05)
  signif <- signif[order(signif$p),]
  if("Drug_Gene" %in% grouping) {
    signif$InG2P <- ifelse(signif$Drug_Gene %in% g2p_dg, "Yes", "No")
  }
  if("Drug_Gene_Lin" %in% grouping) {
    signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_dgl, "Yes", "No")
  }
  saveRDS(signif, outfile)
  return(signif)
}
```

```{r wilcoxon_tests, eval=FALSE}
crispr <- unfactorize(crispr)
crispr_signif_all_gene <- WilcoxonTestDF(dataframe = crispr, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g.rds")
crispr_filt <- filter(crispr, Gene %in% g2p_genes)
crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_filt, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_g.rds")
crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_filt, grouping = c("Gene", "disease"), outfile = "./data_munging/rds/crispr_signif_g2p_gl.rds")

ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_genes)
ccle_filt$Gene <- factor(ccle_filt$Gene, ordered = FALSE)
ccle_filt <- unfactorize(ccle_filt)
ccle_signif_dg <- WilcoxonTestDF(dataframe = ccle, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ccle_signif_dg.rds")
ccle_signif_g2p_dg <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ccle_signif_g2p_dg.rds")
ccle_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ccle_signif_g2p_dgl.rds")

ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_genes)
ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
ctrp_filt <- unfactorize(ctrp_filt)
ctrp_signif_dg <- WilcoxonTestDF(dataframe = ctrp, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_dg.rds")
ctrp_signif_g2p_dg <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_g2p_dg.rds")
ctrp_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ctrp_signif_g2p_dgl.rds")

gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_genes)
gdsc_filt$Gene <- factor(gdsc_filt$Gene, ordered = FALSE)
gdsc_filt <- unfactorize(gdsc_filt)
gdsc_signif_dg <- WilcoxonTestDF(dataframe = gdsc, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_dg.rds")
gdsc_signif_g2p_dg <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_g2p_dg.rds")
gdsc_signif_g2p_dgl <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/gdsc_signif_g2p_dgl.rds")
```

```{r load_wilcoxon_rds}
# crispr_signif_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
# crispr_signif_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")

# ccle_signif_gene <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
# ccle_signif_g2p_druggene <- readRDS("./data_munging/rds/ccle_signif_g2p_druggene.rds")
# ccle_signif_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
# 
# ctrp_signif_gene <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
# ctrp_signif_g2p_druggene <- readRDS("./data_munging/rds/ctrp_signif_g2p_druggene.rds")
# ctrp_signif_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
# 
# gdsc_signif_gene <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
# gdsc_signif_g2p_druggene <- readRDS("./data_munging/rds/gdsc_signif_g2p_druggene.rds")
# gdsc_signif_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
```

@@

```{r drug_spear_calc, warning=FALSE, eval=FALSE}
g2p_druggene_tally <- g2p %>% group_by(Drug_Gene) %>% tally() %>% drop_na()

# CCLE
ccle_ge_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>% summarize(
                GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
                GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value)
ccle_cn_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(
                CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
                CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
ccle_cor_res <- merge(g2p_druggene_tally, merge(ccle_ge_res, ccle_cn_res, by = c("Drug", "Gene", "Drug_Gene"), all = TRUE), by = "Drug_Gene", all.y = TRUE)
ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
ccle_cor_res$Dataset <- "CCLE"

>>>>

g2p_dgl <-  as.character(unique(g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)]))
g2p_dg <- as.character(unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)]))
g2p_gl <- as.character(unique(g2p$Gene_Lin[!is.na(g2p$Gene_Lin)]))
g2p_drugs <- as.character(unique(g2p$Drug[!is.na(g2p$Drug)]))
g2p_genes <- as.character(unique(g2p$Gene[!is.na(g2p$Gene)]))
g2p_dg_genes <- unique(sapply(strsplit(g2p_dgl, "_", fixed = TRUE), function(x) x[2]))
g2p_lins <- as.character(unique(g2p$group_general_lineage_name[!is.na(g2p$group_general_lineage_name)]))

g2p$biomarker_type_curated <- ifelse(is.na(g2p$biomarker_type_curated), "None", as.character(g2p$biomarker_type_curated))
g2p_split <- split(g2p, g2p$biomarker_type_curated)
g2p_amp <- g2p_split[[1]]
g2p_expr <- g2p_split[[2]]
g2p_fus <- g2p_split[[3]]
g2p_fus$FusionPair <- sapply(X = g2p_fus$Feature.Names, function(x) strsplit(as.character(x)," ")[[1]][1])
g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "Fusions", as.character(g2p_fus$Gene), as.character(g2p_fus$FusionPair))
g2p_mut <- g2p_split[[4]]
g2p_mut_genes <- unique(sapply(strsplit(as.character(g2p_mut$Drug_Gene)[!is.na(g2p_mut$Drug_Gene)], "_", fixed = TRUE), function(x) x[2]))
g2p_no_biomarker <- g2p_split[[4]]

g2p_nodrug <- filter(g2p, is.na(Drug))
```

@@

```{r fusion_calls, eval=TRUE}
fusions <- read.delim("./data_munging/19Q2/CCLE_fusions.csv.gz", header = TRUE, sep = ",")
fusions$LeftGene <- gsub(" .*", "", fusions$LeftGene)
fusions$RightGene <- gsub(" .*", "", fusions$RightGene)
fusions$X.FusionName <- gsub("--", "-", fusions$X.FusionName)
fusions <- select(fusions, DepMap_ID, X.FusionName, LeftGene, RightGene)
fusions <- as.data.frame(lapply(fusions, function(x) gsub("IGH@|IGH-@", "IGH", x)))
colnames(fusions) <- c("DepMap_ID", "FusionPair", "LeftGene", "RightGene")
fusions <- merge(fusions, ccl_meta, by = "DepMap_ID", all.x = TRUE)
fusions$G2P_Fusion <- ifelse(fusions$FusionPair %in% as.character(unique(g2p_fus$FusionPair)) | fusions$LeftGene %in% as.character(unique(g2p_fus$FusionPair)) | fusions$RightGene %in% as.character(unique(g2p_fus$FusionPair)), "Yes", "No")
fusions_filt <- unique(filter(fusions, G2P_Fusion == "Yes"))
```

@@

Merge fusions:
```{r, eval=FALSE}
ccle_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/CCLE_drug_response_metrics.csv.gz", sep = ",")
ctrp_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/CTRP_drug_response_metrics.csv.gz", sep = ",")
gdsc_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/GDSC_drug_response_metrics.csv.gz", sep = ",")

ccle_fus <- auc %>% filter(Database == "CCLE") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, AUC_IC50)
ccle_fus_grid <- expand.grid("DepMap_ID" = unique(ccle_fus$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
ccle_fus <- merge(merge(ccle_fus, ccle_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
ccle_fus$G2P_Fusion <- ifelse(is.na(ccle_fus$G2P_Fusion), "No", as.character(ccle_fus$G2P_Fusion))

ctrp_fus <- auc %>% filter(Database == "CTRP") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, AUC_IC50)
ctrp_fus_grid <- expand.grid("DepMap_ID" = unique(ctrp_fus$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
ctrp_fus <- merge(merge(ctrp_fus, ctrp_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
ctrp_fus$G2P_Fusion <- ifelse(is.na(ctrp_fus$G2P_Fusion), "No", as.character(ctrp_fus$G2P_Fusion))

gdsc_fus <- auc %>% filter(Database == "GDSC") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, AUC_IC50)
gdsc_fus_grid <- expand.grid("DepMap_ID" = unique(gdsc_fus$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
gdsc_fus <- merge(merge(gdsc_fus, gdsc_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
gdsc_fus$G2P_Fusion <- ifelse(is.na(gdsc_fus$G2P_Fusion), "No", as.character(gdsc_fus$G2P_Fusion))

fus <- bind_rows(ccle_fus, ctrp_fus, gdsc_fus)
saveRDS(fus, "./data_munging/rds/fusions_merged.rds")
```

```{r}
fus <- readRDS("./data_munging/rds/fusions_merged.rds") %>% drop_na(Drug)
fus_summary <- fus %>% count(Drug, FusionPair, G2P_Fusion)
```

@@

# Define color scale
col_fun <- colorRamp2(c(0, 1, 100), c("gray97", "mistyrose", "purple4"))
# Legend properties list
ht_legend_list <- list(legend_direction = "horizontal", legend_width = unit(2.5, "in"), border = "gray70")
ht <- Heatmap(g2p_dg_counts, 
              name = "Number of G2P interpretations",
              col = col_fun,
              na_col = "gray97",
              rect_gp = gpar(col = "gray70"),
              heatmap_legend_param = ht_legend_list,
              cluster_rows = FALSE, 
              cluster_columns = FALSE, 
              show_row_names = FALSE,
              row_names_side = "left",
              row_names_gp = gpar(fontsize = 10),
              column_names_side = "bottom",
              show_column_names = FALSE,
              bottom_annotation = HeatmapAnnotation(
                  text = anno_text(colnames(g2p_dg_counts),
                                   rot = 45,
                                   gp = gpar(fontsize = 8),
                                   offset = unit(1, "npc"),
                                   just = "right"),
                  annotation_height = unit(0.45, "in")),
              row_title = "Drugs",
              row_title_gp = gpar(fontface = "bold", fontsize = 14),
              column_title = "Genes", 
              column_title_gp = gpar(fontface = "bold", fontsize = 14),
              column_title_side = "bottom")

@@

WilcoxonTestDF <- function(dataframe, grouping, g2p_list, outfile) {
  require(ggpubr)
  if("Drug_Gene_Lin" %in% grouping) {
    # Filter out DGLs with too few samples in at least one mutation status category
    count_mut_n <- dataframe %>% count(Drug_Gene_Lin, Mutation) %>% filter(n >= 3)
    count_mut_category <- count_mut_n %>% count(Drug_Gene_Lin) %>% filter(n == 2)
    dgl_keep <- intersect(count_mut_n$Drug_Gene_Lin, count_mut_category$Drug_Gene_Lin)
    dataframe <- filter(dataframe, Drug_Gene_Lin %in% dgl_keep)
    dataframe$Drug_Gene_Lin <- as.character(dataframe$Drug_Gene_Lin)
  }
  signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
  signif <- adj_signif(signif, alpha = 0.05)
  signif <- signif[order(signif$p),]
  if("Drug_Gene" %in% grouping) {
    signif$InG2P <- ifelse(signif$Drug_Gene %in% g2p_list, "Yes", "No")
  }
  if("Drug_Gene_Lin" %in% grouping) {
    signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_list, "Yes", "No")
  }
  saveRDS(signif, outfile)
  return(signif)
}
```

```{r}
test <- unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)]))
test2 <- unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)]))
```

```{r wilcoxon_tests, eval=FALSE}
crispr <- unfactorize(crispr)
# crispr_signif_all_gene <- WilcoxonTestDF(dataframe = crispr, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g.rds")
crispr_filt <- filter(crispr, Gene %in% g2p_genes)
crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_filt, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_g.rds")
crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_filt, grouping = c("Gene", "disease"), outfile = "./data_munging/rds/crispr_signif_g2p_gl.rds")

ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
ccle_filt$Gene <- factor(ccle_filt$Gene, ordered = FALSE)
ccle_filt <- unfactorize(ccle_filt)
ccle_signif_dg <- WilcoxonTestDF(dataframe = ccle, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ccle_signif_dg.rds")
ccle_signif_g2p_dg <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ccle_signif_g2p_dg.rds")
ccle_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/ccle_signif_g2p_dgl.rds")

ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
ctrp_filt <- unfactorize(ctrp_filt)
# ctrp_signif_dg <- WilcoxonTestDF(dataframe = ctrp, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ctrp_signif_dg.rds")
ctrp_signif_g2p_dg <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ctrp_signif_g2p_dg.rds")
ctrp_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/ctrp_signif_g2p_dgl.rds")

gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
gdsc_filt$Gene <- factor(gdsc_filt$Gene, ordered = FALSE)
gdsc_filt <- unfactorize(gdsc_filt)
# gdsc_signif_dg <- WilcoxonTestDF(dataframe = gdsc, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/gdsc_signif_dg.rds")
gdsc_signif_g2p_dg <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/gdsc_signif_g2p_dg.rds")
gdsc_signif_g2p_dgl <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/gdsc_signif_g2p_dgl.rds")
```

```{r load_wilcoxon_rds}
crispr_signif_g <- readRDS("./data_munging/rds/crispr_signif_g.rds")
crispr_signif_g2p_g <- readRDS("./data_munging/rds/crispr_signif_g2p_g.rds")
crispr_signif_lin <- readRDS("./data_munging/rds/crispr_signif_g2p_gl.rds")

ccle_signif_dg <- readRDS("./data_munging/rds/ccle_signif_dg.rds")
ccle_signif_g2p_dg <- readRDS("./data_munging/rds/ccle_signif_g2p_dg.rds")
ccle_signif_dgl <- readRDS("./data_munging/rds/ccle_signif_g2p_dgl.rds")

# ctrp_signif_g <- readRDS("./data_munging/rds/ctrp_signif_dg.rds")
ctrp_signif_g2p_dg <- readRDS("./data_munging/rds/ctrp_signif_g2p_dg.rds")
ctrp_signif_dgl <- readRDS("./data_munging/rds/ctrp_signif_g2p_dgl.rds")

# gdsc_signif_g <- readRDS("./data_munging/rds/gdsc_signif_dg.rds")
gdsc_signif_g2p_dg <- readRDS("./data_munging/rds/gdsc_signif_g2p_dg.rds")
gdsc_signif_dgl <- readRDS("./data_munging/rds/gdsc_signif_g2p_dgl.rds")
```

## Plots

```{r fig.height=4, fig.width=8}
crispr_filt <- filter(crispr, Gene %in% g2p_mut_genes)
crispr_filt$Gene <- factor(crispr_filt$Gene, levels = g2p_mut_genes)
crispr_filt$Mutation <- as.character(crispr_filt$Mutation)
crispr_signif_filt <- filter(crispr_signif_g2p_g, Gene %in% g2p_mut_genes)
crispr_signif_filt$Gene <- factor(crispr_signif_filt$Gene, levels = g2p_mut_genes)

crispr_gene_mut_plot <- ggplot(data = crispr_filt) +
  facet_wrap(~ Gene, nrow = 2, drop = FALSE) +
  scale_color_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
  scale_x_discrete(name = "Mutation Status", labels = c("0" = "WT", "1" = "Mut")) +
  geom_jitter(aes(x = Mutation, y = Score, color = Mutation), width = 0.2, alpha = 0.5, size = 0.6) +
  geom_boxplot(aes(x = Mutation, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
  geom_text(data = crispr_signif_filt, aes(x = 1.5, y = 2, label = p.signif)) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  theme(legend.position = "top", legend.direction = "horizontal") +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y = "CERES Score")
crispr_gene_mut_plot

# ggsave("./plots/manuscript/crispr_gene_mut_plot.png", crispr_gene_mut_plot, width = 12, height = 6, units = "in")
```

```{r}
MakeMutHeatmap <- function(signif_g2p_dg, row_names, col_title, color, legend_title) {
  signif_grid <- dcast(signif_g2p_dg, Gene ~ Drug, value.var = "p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
  signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
  signif_grid <- signif_grid[complete.cases(signif_grid), ]
  signif_grid[signif_grid > 0.05] <- NA

  signif_grid_annot <- dcast(signif_g2p_dg, Gene ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
  signif_grid_annot <- signif_grid_annot[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
  signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
  signif_grid_annot[signif_grid_annot == "No"] <- ""
  signif_grid_annot[signif_grid_annot == "Yes"] <- "O"

  col_fun <- colorRamp2(c(0, 0.05), c(color, "gray97"))
  # Legend properties list
  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70",   at = seq(0, 0.05, by = 0.01), labels = seq(0, 0.05, by = 0.01))
  ht <- Heatmap(signif_grid,
                col = col_fun,
                na_col = "gray97",
                rect_gp = gpar(col = "gray70"),
                heatmap_legend_param = ht_legend_list,
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                show_row_names = as.logical(row_names),
                row_names_side = "left",
                row_names_gp = gpar(fontsize = 10),
                column_names_side = "bottom",
                column_names_gp = gpar(fontsize = 10),
                show_column_names = FALSE,
                bottom_annotation = HeatmapAnnotation(
                  text = anno_text(colnames(signif_grid),
                                   rot = 45,
                                   gp = gpar(fontsize = 11),
                                   offset = unit(1, "npc"),
                                   just = "right"),
                  annotation_height = unit(0.85, "in")),
                  # annotation_height = max_text_width(colnames(signif_grid))),
                row_title = "Genes",
                row_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title = col_title, 
                column_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title_side = "bottom",
                cell_fun = function(j, i, x, y, width, height, fill) {
                  grid.text(signif_grid_annot[i, j], x, y, gp = gpar(fontsize = 20))
                  # if(signif_grid_annot[i, j] == "G") {
                  #   grid.circle(x = x, y = y, r = 0.02, gp = gpar(fill = "transparent", col = "black"))
                  # }
                }
                )
  return(ht)
}
```

```{r mut_heatmaps, eval=FALSE}
ht_ccle <- MakeMutHeatmap(signif_g2p_dg = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "P-value", row_names = TRUE, color = "darkgreen", col_title = "Drugs")
png(filename = "./plots/manuscript/ccle_mut_heatmap.png", width = 3, height = 10, units = "in", res = 500)
draw(ht_ccle, heatmap_legend_side = "top")
dev.off()

ht_ctrp <- MakeMutHeatmap(signif_g2p_dg = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "P-value", row_names = TRUE, color = "steelblue4", col_title = "Drugs")
png(filename = "./plots/manuscript/ctrp_mut_heatmap.png", width = 9.5, height = 10, units = "in", res = 500)
draw(ht_ctrp, heatmap_legend_side = "top")
dev.off()

ht_gdsc <- MakeMutHeatmap(signif_g2p_dg = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "P-value", row_names = TRUE, color = "turquoise4", col_title = "Drugs")
png(filename = "./plots/manuscript/gdsc_mut_heatmap.png", width = 5, height = 10, units = "in", res = 500)
draw(ht_gdsc, heatmap_legend_side = "top")
dev.off()

ht_ccle2 <- MakeMutHeatmap(signif_g2p_dg = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "CCLE p-value                                                                               ", row_names = TRUE, color = "darkgreen", col_title = "")
ht_ctrp2 <- MakeMutHeatmap(signif_g2p_dg = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "CTRP p-value                                                                              ", row_names = FALSE, color = "steelblue4", col_title = "Drugs")
ht_gdsc2 <- MakeMutHeatmap(signif_g2p_dg = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "GDSC p-value", row_names = FALSE, color = "turquoise4", col_title = "")
png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 10, units = "in", res = 500)
draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
dev.off()
```

# WILCOXON (Fusions)

@@

```{r drug_spear_calc, warning=FALSE, eval=FALSE}
# CCLE
ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_genes)
ccle_filt$Gene <- factor(ccle_filt$Gene, ordered = FALSE)
ccle_filt <- unfactorize(ccle_filt)
ccle_ge_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>% summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate, GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value)
ccle_ge_res$InG2P <- ifelse(ccle_ge_res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
ccle_ge_res$Dataset <- "CCLE"
ccle_cn_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate, CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
ccle_cn_res$InG2P <- ifelse(ccle_cn_res$Drug_Gene %in% unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])), "Yes", "No")
ccle_cn_res$Dataset <- "CCLE"

# CTRP
ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_genes)
ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
ctrp_filt <- unfactorize(ctrp_filt)
ctrp_ge_res <- ctrp_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>% summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate, GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value)
ctrp_ge_res$InG2P <- ifelse(ctrp_ge_res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
ctrp_ge_res$Dataset <- "CTRP"
ctrp_cn_res <- ctrp_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate, CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
ctrp_cn_res$InG2P <- ifelse(ctrp_cn_res$Drug_Gene %in% unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])), "Yes", "No")
ctrp_cn_res$Dataset <- "CTRP"
